---
title: "Pitch Presentation of the Shiny App - Prediction of Miles Per Gallon"
author: "Lin Htet Naing"
date: "9/3/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
- Prediction of Miles Per Gallon by Horsepower and/or Weight of a car is a course project for Data Science - Developing Data Products course.
- The data is from "mtcars" dataset which was extracted from the 1974 Motor Trend US magazine.
- Fuel consumption expressed as miles per gallon (mpg) is predicted from gross horsepower (hp) and weight (wt) of a car.

## Models for prediction
Three linear models were fit:

 Model 1 - Miles per gallon (mpg) vs Horsepower (hp)
 
 Model 2 - Miles per gallon (mpg) vs Weight (wt)
 
 Model 3 - Miles per gallon (mpg) vs Horsepower (hp) and Weight (wt)

These models were used to predict mpg from horsepower or weight or both. 

## Using the application
Shiny application can be found here: <https://linhtetnaing.shinyapps.io/CourseProject/>.

In the application,

- horsepower and weight are available to be selected in the sidebar panel.
- once selected, it is required to click submit button.
- in the main panel, scatter plots showing relation between mpg and horsepower, and mpg and weight (in 1000 pounds) are shown.
- a related regression line is also included in each graph.
- under the graphs, predictions of miles per gallon (calculated from the inputs) are shown in textboxes - using "reactive()".


## Scatter plots (mpg vs hp, mpg vs wt)
```{r cars, echo = FALSE}
library(datasets)
data("mtcars")
    model1 <- lm(mpg ~ hp, data = mtcars)
    model2 <- lm(mpg ~ wt, data = mtcars)
par(mfrow=c(1,2))
 plot(mtcars$hp, mtcars$mpg, main = "Miles per gallon vs Horsepower", xlab = "Horsepower",
             ylab = "Miles Per Gallon",
             pch = 16)
        abline(model1, col = "red", lwd = 2)
        
 plot(mtcars$wt, mtcars$mpg, main = "Miles per gallon vs Weight", xlab = "Weight (in 1000 pounds)",
             ylab = "Miles Per Gallon",
             pch = 16)
        abline(model2, col = "blue", lwd = 2)
```

The ui.R and server.R files can be found here:
<https://github.com/LinHtetNaing/DataProducts.git>.